Extending Graphical Representations for Compact Closed Categories with Applications to Symbolic Quantum Computation

### 2008-05-03 papers/reasoning-graphically/paper.tex
tiny thing on keywords fixed.
git-svn-id: https://isaplanner.svn.sourceforge.net/svnroot/isaplanner/trunk/quantomatic@1479 f8f375fb-4f10-0410-8d47-b6fbdc7ca053

  \keywords{graph rewriting, quantum computing, categorical logic,
    interactive theorem proving, graphical calculi; concerning:
    symbolic computation, automated reasoning, formal mathematics.}
\end{abstract}

>>>>

  \keywords{graph rewriting, quantum computing, categorical logic,
    interactive theorem proving, graphical calculi.}
% concerning:
%    symbolic computation, automated reasoning, formalised mathematics.
\end{abstract}
